Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-11 krs-survey.tex
Filled section on lazy evaluation

>>>>

\emph{Lazy evaluation} describes the ability for a KRS to delay active
knowledge acquisition or resoning operations until the value is actually
needed.

For instance, a system that computes the symbolic relative placement of two
objects only when this fact is required to answer a query would be said to
adopt a lazy evaluation strategy, whereas a system that computes {\it a priori}
such relations (and by consequence, carries out such computation for possibly
all known objects) would be said to use a \emph{strict evaluation} policy.

Lazy evaluation has an immediate impact on efficiency and scalability of the
system, and some problems may even be only tractable with a lazy evaluation
strategy (the relative placements of object is an example of combinatory
explosion in strict evaluation approaches, although this issue is mitigated in
real use-cases by heuristics that select a subset of objects to evaluate).

One downside is that the knowledge base never contains explicitly the complete
set of beliefs of the robot. This limits for instance the ability for the robot
to react to logical conditions that involves fact that are lazily evaluated
(``trigger a callback when object A is behind object B'' could be an example of
a event triggered by a logical condition).
